---
title: "Disappearing Dogs"
author: "Ben Schmidt"
date: "4/16/2021"
output: html_document
---

All dogs go to heaven, but some really do go upstate first.

This study looks at "survivorship" in the statistical and the real sense by
seeing what dogs disappear from the New York City license registry. 
If a dog shows up in one year, does its license get renewed in later years?
What affects that 
decision? Logistic regression allows us to consider age, breed, and gender as separate factors. Knowing what breeds are likely vanish could guide dog buyers in thinking about
what puppies might be unhappy in the city, and perhaps help dog actuaries better
plan the dog annuities on dog life insurance policies. (This is an especially
important question because dog annuitities pay out 
7 times as much year as human annuities.)

# Data creation

We start with the full dog name list, and filter down to clean names and exclude any duplicate licenses.

We then filter the criteria that are useful for identifying individual jobs or that 
we think might affect retention.

```{r setup, include=FALSE}
source("R/utils.R")
source("R/loading.R")

candidates = load_dogs() %>% 
  exclude_duplicate_licenses() %>% only_clean_names

subset = candidates %>%
  select(AnimalGender, AnimalBirthMonth, BreedName, `Extract Year`, AnimalName, ZipCode)
```

Next, we build two separate frame: a reference set of all the dogs in 2016, and then a
comparison set of all the dogs in the 2017 and 2018 dumps with difference licenses.

The question will be: how many dogs persist from one to the other? By doing a left_join
from the reference to the outcome corpus, we get a column that indicates for each dog
whether it existed in 2017.

```{r}

reference = subset %>%
  filter(`Extract Year` == 2016)

# From outcome, select only the factors we need to match into the 2016 set.
outcome = subset %>%
  filter(`Extract Year` >= 2017) %>% 
  select(BreedName, ZipCode, AnimalName) %>%
  mutate(in_2018 = TRUE)

modelable = reference %>% left_join(outcome) %>%
  mutate(in_2018 = in_2018 %>% replace_na(FALSE))

modelable %>% count(AnimalGender, in_2018)
```

This data is now suitable for logistic regression. We filter to dogs between 0 and 18, only looking at the 25 most common breeds.
```{r}
modelable = modelable %>%
  mutate(age = 2016 - AnimalBirthMonth) %>%
  mutate(BreedName = fct_lump(BreedName, 35) %>% relevel("Unknown")) %>%
  filter(age < 19, age >= 0)
  
  
model = glm(in_2018 ~ factor(age) + BreedName + AnimalGender + 0, data = modelable, family = "binomial")
```

We can look at the summaries here. These regression coefficients show significance as stars.

```{r}
model %>% summary
```

Tidyverse provides a method to sweep these up. We can see the factors that make a dog especially likely to stay in the set (being 7, 8, or 9; heing a Havanese or Shih Tzu)
and those that make a dog especially likely to vanish (being very young, or a pit bull; marginally more likely if male rather than female.)

```{r}
model %>%
  broom::tidy() %>%
  arrange(-estimate) %>%
  ggplot() +
  geom_errorbar(aes(x = reorder(term, estimate), ymin = estimate - std.error, ymax=estimate + std.error )) + coord_flip()
```

